\documentclass{article}

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with `a4paper' for UK/EU standard size
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{setspace}
\doublespacing

\title{Problem Set 1}
\author{Beth Felkner}

\begin{document}
\maketitle

\section{My Interests}

I wanted to take this class because I love the problem solving nature of economics and I want to gain mastery of data science tools so that I can gain insight about bigger problems from bigger datasets. I am very interested in environmental economics, especially relating to climate justice and renewable energy transition. For the final project, I want to do something with the environmental dataset you've shared with me, and potentially joining it with some of my own data as well. I have not exactly decided what relationship(s) I want to look at, but I am thinking something about the relationship between environmental conditions and educational attainment because this would be an interesting expansion of my previous project about the relationship between income and air quality. I have a decent background in the econometric analysis side of data science from previous classes and my internship, but I would like to further strengthen my coding skills in this class. What I am not good at, and thus my primary learning goal in this class, is how to obtain a dataset upon which to apply econometric methods. Specifically I would like to learn about web-scraping and about how to clean datasets and join data from various sources. My plan for after graduation is that I have accepted a Business Analytics position at Williams which is a F500 natural gas company. My first rotational will be in the GIS department and from my understanding I will be primarily using SQL in that role. I am excited for this job because I believe that natural gas is an important intermediary step in the transition towards lower emission energy sources.

\section{Equation}
\[ a^2 + b^2 = c^2 \]

\end{document}